implementation quality control

### 2018-02-26 analysis/analyses/4-method_characterisation/7_quality_control.Rmd
small update to method characterisation

Calculate the overall qc scores for each implementation
```{r}
# set the ordering of implementation_ids to this ordering
implementation_ordering_plot <- implementations_evaluated %>%
  arrange(-qc_score) %>% 
  mutate(implementation_id = factor(implementation_id, levels=implementation_id)) %>% 
  ggplot(aes(implementation_id, qc_score)) +
    geom_bar(aes(fill=qc_score), stat="identity") +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
    scale_y_continuous(expand=c(0, 0), limits=c(0, 1)) +
    viridis::scale_fill_viridis(option="A", limits=c(0, 1))

implementation_ordering_plot
```

@@

implementation_qc_ordering_plot <- cowplot::plot_grid(category_legend, aspect_ordering_plot2, align = "h", rel_widths = c(0.2, 0.8), axis="tb")
implementation_qc_ordering_plot
saveRDS(implementation_qc_ordering_plot, figure_file("implementation_qc_ordering.rds"))
```

>>>>

Calculate the overall qc scores for each implementation
```{r}
# set the ordering of implementation_ids to this ordering
implementation_ordering_plot <- implementations_evaluated %>%
  arrange(-qc_score) %>% 
  mutate(implementation_name = factor(implementation_name, levels=implementation_name)) %>% 
  ggplot(aes(implementation_name, qc_score)) +
    geom_bar(aes(fill=qc_score), stat="identity") +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
    scale_y_continuous(expand=c(0, 0), limits=c(0, 1)) +
    viridis::scale_fill_viridis(option="A", limits=c(0, 1)) +
    labs(y=label_long("qc_score"), x=label_long("implementation_name")) +
    theme(legend.position="none")

implementation_ordering_plot
implementation_ordering_plot %>% write_rds(figure_file("implementation_qc_ordering.rds"))
```

@@

implementation_qc_ordering_plot <- cowplot::plot_grid(category_legend, aspect_ordering_plot2, align = "h", rel_widths = c(0.2, 0.8), axis="tb")
implementation_qc_ordering_plot
saveRDS(implementation_qc_ordering_plot, figure_file("implementation_qc_issues.rds"))
```
